On the presentation of orthogonal groups over polynomial rings

### 2019-08-08 dl-paper.tex
Fixes

\begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective. \end{corollary}
\begin{proof} Follows from consideration of the following commutative diagram:
\[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}]),} \]
in which the left arrow is an isomorphism by the Korollar of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}. \end{proof}

@@

This action satisfies the following additional property. If $v = (g, [h], u) \in \overline{V}$ is such that $\overline{p}(v) = \overline{1} = G_M^0$ then for any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_-(h_1) \cdot v = (h_1 \cdot g, [h \cdot h_1^{-1}], u)$ and, moreover, $\overline{p}(j_-(h_1) \cdot v) = \overline{1}$.
\end{prop}
\begin{proof}
  By~\cref{superfluous-relations} and Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined. On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} (set $t = X^{-1}$).

@@

\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.}
We retain notation of the previous subsection and assume additionally that the map $\St(\Phi, B) \to \St(\Phi, R)$ is injective. This assumption allows us to consider $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
%Denote by $I$ the ideal $M[X, X\inv]$ of $B$ (it is also an ideal of $R$).
Notice that by~\cref{lem:lemma32} the subgroup $\overline{G}^{\geq 0}_M$ is contained in $\St(\Phi, B)$.

@@

\begin{theorem}
 If $\Phi$ is as in the statement of~\cref{lemma33}, then the map $j_-$ is injective.
 If, moreover, $\St(\Phi, A[X]) \to \St(\Phi, B)$ is injective, then the following square is pullback
 \begin{equation} \nonumber
  \xymatrix{ \St(\Phi, A) \ar[r] \ar[d] & \St(\Phi, A[X]) \ar[d]^{j_+} \\ \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, R).}
 \end{equation}
\end{theorem}
\begin{proof}
 Let us show that $j_-$ is injective. Set $v_0 = (1, [1], 1) \in \overline{V}$ and suppose $g \in \Ker(j_-)$.
 By~\cref{prop43} holds $v_0 = j_-(g) \cdot v_0 = (g, [g^{-1}], u)$ therefore $g \in G_M^0$ and consequently $g=1$.

 Now suppose $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_-(g_-) = j_+(g_-)$. From~\cref{field-injectivity} it follows that the image $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$. Dividing $g_+$ and $g_-$ by $g_0$ we can achieve
\end{proof}

\printbibliography

\end{document}

>>>>

\begin{corollary} \label{field-injectivity} For $\Phi\neq\rG_2$ the map $\St(\Phi, k[X]) \to \St(\Phi, k[X, X^{-1}])$ is injective. Moreover, the intersection of images of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$ coincides with the image of $\St(\Phi, k)$. \end{corollary}
\begin{proof} The first assertion follows from consideration of the following commutative diagram:
\[\xymatrix{ & \K_2(\Phi, k) \ar[dl]_{\cong} \ar@{^{(}->}[dr] & \\
               \K_2(\Phi, k[X]) \ar[rr] &               & \K_2(\Phi, k[X, X^{-1}]),} \]
in which the left arrow is an isomorphism by the Korollar of~\cite[Satz~1]{Re75} and the right arrow is split injective by~\cref{K2-laurent-field}.

Let us verify the second assertion. Let $g$ be an element of the intersection of $\St(\Phi, k[X])$ and $\St(\Phi, k[X\inv])$ inside $\St(\Phi, k[X, X\inv])$.
Clearly, the image of $g$ in $G(\Phi, k[X, X\inv])$ lies in $G(\Phi, k)$, therefore there exists $g_0 \in \St(\Phi, k)$ such that $gg_0^{-1} \in \K_2(\Phi, k[t]) = \K_2(\Phi, k)$. Thus, we conclude that $g \in \St(\Phi, k)$.
\end{proof}

@@

This action satisfies the following additional property. If $v = (g, [h], u) \in \overline{V}$ is such that $\overline{p}(v) = \overline{1} = G_M^0$ then for any $h_1 \in \St(\Phi, A[X\inv])$ holds $j_B(h_1) \cdot v = (h_1 \cdot g, [h \cdot h_1^{-1}], u)$ and, moreover, $\overline{p}(j_B(h_1) \cdot v) = \overline{1}$. Here $j_B$ denotes the obvious map $\St(\Phi, A[X\inv]) \to \St(\Phi, B)$.
\end{prop}
\begin{proof}
  By~\cref{superfluous-relations} and Lemmas~\ref{R3_leq0_1}--\ref{R2_0_1} the action of $\St^{\leq 1}(\Phi, B)$ on $\overline{V}$ given by~\eqref{T_1} and~\eqref{T_leq0} is well-defined. On the other hand, the group $\St^{\leq 1}(\Phi, B)$ is isomorphic to $\St(\Phi, B)$ by~\cref{lemma33} (set $t = X^{-1}$).

@@

\subsection{Proof of the $\mathbb{P}^1$-glueing theorem.}
We retain notation of the previous subsection and assume additionally that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, R)$ is injective. This assumption allows us to consider $\St(\Phi, B)$ as a subgroup of $\St(\Phi, R)$.
%Denote by $I$ the ideal $M[X, X\inv]$ of $B$ (it is also an ideal of $R$).
Notice that by~\cref{lem:lemma32} the subgroup $\overline{G}^{\geq 0}_M$ is contained in $\St(\Phi, B)$.

@@

\begin{theorem}
 Let $\Phi$ be a root system of type $\rA_{\geq 4}, \rD_{\geq 5}$ or $\rE_{6,7,8}$.
 %Suppose that the map $j_R \colon \St(\Phi, B) \to \St(\Phi, A[X, X\inv])$ is injective.  
 Then the map $j_-$ is injective and the following commutative square is pullback
 \begin{equation} \nonumber
  \xymatrix{ \St(\Phi, A) \ar[r] \ar[d] & \St(\Phi, A[X]) \ar[d]^{j_+} \\ \St(\Phi, A[X\inv]) \ar[r]^{j_-} & \St(\Phi, A[X, X\inv]).}
 \end{equation}
\end{theorem}
\begin{proof}
 Since $j_- = j_R j_B$, where $j_B$ is as in~\cref{prop43}, it suffices to show that $j_B$ is injective.
 Set $v_0 = (1, [1], 1) \in \overline{V}$ and suppose $g \in \Ker(j_B)$.
 By~\cref{prop43} holds $v_0 = j_B(g) \cdot v_0 = (g, [g^{-1}], u)$ therefore $g \in G_M^0$ and consequently $g = 1$.

 Now suppose $g_+ \in \St(\Phi, A[X])$ and $g_- \in \St(\Phi, A[X\inv])$ are such that $j_-(g_-) = j_+(g_-)$. From~\cref{field-injectivity} it follows that the image $j_+(g_+) = j_-(g_-)$ in $\St(\Phi, k[X, X\inv])$ belongs to $\St(\Phi, k)$ and therefore coincides with the image in $\St(\Phi, k)$ of some $g_0 \in \St(\Phi, A)$. 
 Set $g_+' = g_+g_0^{-1}$ and $g_-' = g_-g_0^{-1}$.
 %Clearly, $g_+' \in \overline{\St}(\Phi, A[X], M[X])$. Set $v = () $
\end{proof}

\printbibliography
\end{document}
